Dissecting Neural Style Transfer

### 2019-05-26 paper/paper.tex
1

Now we wonder, could we achieve similar results with other ways to compare 
distribution of features?
One approach would be to consider the \emph{comparison} as a whole to find 
substitute. 
For us, it seemed more natural to consider substitute to the process of 
transforming feature maps to Gram matrices itself, that is, 
a mapping that removes the spatial information of where features are but retains
the distribution of features like a histogram.

@@

\begin{thebibliography}{8}
\bibitem{nst}
Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
\bibitem{demyst}
Li, Y., Wang, N., Liu, J., \& Hou, X. (2017). Demystifying Neural Style Transfer. IJCAI.
\bibitem{interp}
Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
\bibitem{pytorch}
Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
\end{thebibliography}
\end{document}

>>>>

Now we wonder, could we achieve similar results with other ways to compare 
distribution of features?
One approach would be to consider the \emph{comparison} as a whole to find 
substitutes. 
For example, minimising the mean square errors between two Gram matrices could be seen as 
a special case for minimising a Maximum Mean Discrepancy, which means other Maximum Mean Discrepacies
could be used \cite{MMD}.
For us, it seemed more natural to consider substitutes for the process itself of 
transforming a feature map into a Gram matrix. 
That is, we will consider other
mappings that remove the spatial information of where features are but retains
the distribution of features, like a histogram.
We will call such functions ``\emph{dislocators}'' in the remaing part of this work.
Unfortunately, the word ``dislocate'' would give the connotation of moving something to somewhere else.
However, the word ``locator'' means something that provides spatial information,
so calling somthing that removes spatial information a ``dislocator'' is still plausible.

Some ``dislocator'' functions we tried are

@@

\begin{thebibliography}{8}
\bibitem{nst}
Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
\bibitem{MMD}
Li, Y., Wang, N., Liu, J., \& Hou, X. (2017). Demystifying Neural Style Transfer. IJCAI.
\bibitem{interp}
Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
\bibitem{pytorch}
Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
\end{thebibliography}
\end{document}
